Joint Neighborhood Subgraphs Link Prediction

### 2017-06-30 paper.tex
F

\section{Experiment}
To compare the performance of the JNSL method with other link prediction approaches we follow \cite{matrix-factorization} and use 6 datasets belonging to different domains.
\begin{itemize}
\item \textit{Protein }\cite{protein-protein}: nodes are proteins and edges encodes a thresholded interaction confidence between proteins. It has 2617 nodes and 11855 links with a median degree of 9.1.

\item \textit{Metabolic} \cite{metabolic}: nodes are enzyme and metabolites, edges are present if the enzyme catalyzes for a reaction that include those chemical compounds. It has 668 nodes and 2782 links with a median degree of 8.3.

\item \textit{Nips} \cite{nips}: nodes are authors at the NIPS conference from the first to the $12^{th}$ edition. Links encode the co-authorhip relation, i.e. if two authors have published a paper together. This network contains 2865 nodes and 4733 links with a median degree of 3.3.

\item \textit{Condmat} \cite{condmat}: nodes are scientists working in condensed matter physics, edges encode co-authorship. This network has 14230 nodes and 1196 links with a median degree of 0.17.

\item \textit{Conflict} \cite{conflict1}, \cite{conflict2}: nodes are countries and edges encode a conflict or a dispute. We have 130 nodes and 180 links in total in this network with a median degree of 2.5.

>>>>

\section{Experiment}
To compare the performance of the JNSL method with other link prediction approaches we follow \cite{matrix-factorization} and use 6 datasets belonging to different domains.
\begin{itemize}
\item \textit{Protein }\cite{protein-protein}: nodes are proteins and edges encodes a thresholded interaction confidence between proteins. It has 2617 nodes and 11855 links with an average degree of 9.1.

\item \textit{Metabolic} \cite{metabolic}: nodes are enzyme and metabolites, edges are present if the enzyme catalyzes for a reaction that include those chemical compounds. It has 668 nodes and 2782 links with an average degree of 8.3.

\item \textit{Nips} \cite{nips}: nodes are authors at the NIPS conference from the first to the $12^{th}$ edition. Links encode the co-authorhip relation, i.e. if two authors have published a paper together. This network contains 2865 nodes and 4733 links with an average degree of 3.3.

\item \textit{Condmat} \cite{condmat}: nodes are scientists working in condensed matter physics, edges encode co-authorship. This network has 14230 nodes and 1196 links with an average degree of 0.17.

\item \textit{Conflict} \cite{conflict1}, \cite{conflict2}: nodes are countries and edges encode a conflict or a dispute. We have 130 nodes and 180 links in total in this network with an average degree of 2.5.
